Inter-Task Effects Induce Bias in Crowdsourcing

### 2014-10-12 docs/publications/2014.08_HCOMP/abridged_man.tex
work on manuscript

%%%%%%%%%%
% Section Numbers
% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0} %%%%%%%%%%
\title{Inter-Task Effects Induce Bias in Crowdsourcing}
\author{Edward Newell\footnote{bla} \and Derek Ruths\\
School of Computer Science, McGill University, Montreal, Canada\\
$^*$\texttt{edward.newell@mail.mcgill.ca}\\
}
%%%%%%%%%%
% Body of Paper Begins
\begin{document}
\maketitle
\section*{Abstract}
Microtask platforms allow researchers to engage participants quickly and 
inexpensively.
Workers on such platforms probably perform many tasks in succession,
so we investigate interactions between earlier tasks and later ones, which we 
call ``inter-task'' effects.  
Existing research investigates many task design factors, such as 
``framing'', on the quality of responses, but to our knowledge, does not 
address inter-task effects.  
We use a canonical image-labeling task on Amazon Mechanical Turk 
to measure the impact of inter-task and framing effects on the focus and 
specificity of labels that workers provide.
We also introduce an algorithmic definition of priming, which measures the 
worst-case bias introduced into responses.
We find that inter-task effects produced a much stronger impact than framing, 
and demonstrate that our novel priming definition yields a generalized 
measure of priming effects when combined with machine learning algorithms.
\paragraph{Keywords:} priming, framing, crowdsourcing.
\section*{Introduction}
Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis,Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a fast and cheap means to engage experimental 
participants in a research 
setting \cite{snow2008cheap}.

@@

Here, we highlight an important way in which HPUs differ from CPUs, with 
serious implications for the design of tasks.  It is well known that people 
are subject to priming effects 
\cite{BJOP1796,No2007,beller1971priming} and, in particular, task-repetition effects
\cite{Gass1999549,sohn2001task}.  
We investigate the effect that previously completed tasks have on workers'
responses during subsequent ones. We call such effects 
\textit{inter-task priming}.  Inter-task priming would amount to a kind of
\textit{hysteresis}, meaning that HPU output is not only a function of the 
current input, but also of the history of inputs.

There has been considerable investigation into the factors that affect the 
quality and quantity of micro-task completion.  These include the level of 
pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, screening of 
workers \cite{paolacci2010running}, and user-interface design 
\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
by testing the effects of disclosing the workflow context 
\cite{Kinnaird2012281}, and the purpose of tasks 
\cite{chandler2013breaking}.  To our knowledge, no study has investigated the 
effects of inter-task priming.

To characterize the effects of inter-task priming, we present a novel  
\textit{algorithmic definition of priming}, and a general method 
for measuring priming effects using machine learning algorithms.  
Rather than focus on internal psychological mechanisms, our definition 
focuses on the impact that priming has to the downstream application of human 
computation, providing a generalized measure of bias.

In the present work, we investigate inter-task priming on the Amazon 
Mechanical Turk platform, using an image-labeling task, one of the most common 
kinds of tasks on that platform 
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  The task requires workers to label ten 
images featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{test set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
We vary the initial set of images, while keeping the test set the same to 
analyze the effect that that the initial images have on the labels that 
workers' attribute to the test set.  We measure effects using our novel 
approach, as well as looking for changes in the content of labels and label 
specificity based on an ontology we developed for that purpose.

As a point of comparison, we subject some groups of workers to a kind of
\textit{framing}: we disclose a fictitious, semantically-loaded name for 
the requester funding the tasks.
The names were chosen to suggest the requester's interest in a specific 
aspect of the image content.  We expect this would cause workers 
to provide more labels, and greater specificity, relating to this 
``preferred'' content.

Surprisingly, we find that inter-task effects are much stronger than the 
framing.  Our results show that initial tasks can significantly alter the 
focus of worker's labels.  Interestingly, we find that inter-task
effects can be used to induce greater specificity.  Our results suggest that
workers attribute more specific labels when labeling a series of images that
that are more similar to one another.  This suggests that careful 
consideration should be given to the bundling of tasks when designing a study 
using a microtask platform.

Our analysis also highlights important advantages of our novel definition of 
priming.  Our approach incorporates no prior knowledge about the nature
of the task whatsoever.  In contrast, we also sought to detect priming
based on its direct effects on label content and specificity,
drawing on prior knowledge about the images and label semantics.
Remarkably, while being more general, our definition yields a more sensitive
measure of priming when combined with machine learning algorithms. 
This approach could be applied to detect priming when one does not 
\emph{a priori} know whether any priming has occurred, 
nor what the nature of the effects might be.
\subsection*{An algorithmic definition of priming}
Our goal in creating a definition of priming is to capture the effects of 
priming on human computation \textit{applications}.  This motivates us to 
seek a definition of priming in terms of its ability alter HPU 
output rather than in terms of psychological mechanisms.

We define priming with respect to a task $\mathcal{T}$.  People will always differ in their initial knowledge, specific 
aptitudes, and in many other intrinsic aspects.  Moreover, priming may not be 
``complete'', in the sense that people's experiences before
priming may continue to have residual effects.  Therefore, we define priming 
in relation to populations, which we regard as having stable distributions of
such latent attributes.

One difficulty in constructing a definition of priming is that there would 
appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  
While arguments could perhaps be made that one treatment or another is 
\textit{more} ``neutral'', we choose to define priming relatively, and speak 
of one treatment being \textit{differently primed} from another.

To set up the definition, when a population of people $\mathcal{P}$ performs
a task $\mathcal{T}$ thus producing outputs $\mathcal{L}$,
we will write $\mathcal{T}(\mathcal{P}) = \mathcal{L}$.

\vspace{2mm}
\begin{mydef}
	\upshape
	Two mutually exclusive populations of people, $\mathcal{P}_0$ and 
	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
	population $\mathcal{P}$, and are exposed to (possibly) different priming 
	treatments. Each population performs a task $\mathcal{T}$, 
	producing outputs $\mathcal{T}(\mathcal{P}_0)$ and 
	$\mathcal{T}(\mathcal{P}_1)$.
	These populations are subsampled, producing 
	$P_0 \subset \mathcal{P}_0$ and
	$P_1 \subset \mathcal{P}_1$. A uniform, random bit is chosen, 
	$b\in _R \{0,1\}$, and a single worker $p$ is uniformly and randomly 
	sampled from 
	$\mathcal{P}_b \setminus P_b$.
	We say that $\mathcal{P}_0$ and $\mathcal{P}_1$ 
	\emph{differ in priming by a degree at least $\theta$},
	if there exists a \emph{distinguisher algorithm} $\mathcal{A}$ that takes as input 
	$\langle\mathcal{T}(J)$, $\mathcal{T}(K)$, $\mathcal{T}(\{p\})\rangle$
	and outputs a guess for $b$ with accuracy $\frac{1+\theta}{2}$.  
\end{mydef}

\begin{figure*}
	\centering{
	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
	\caption{ \footnotesize{
		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
		various treatments.  The difference in priming between each pair of 
		treatments 
		was determined by cross-validation of a Naive Bayes classifier trained
		to classify workers based on the labels they attributed to the first
		image of the test set. Each panel compares a basis treatment,
		indicated above the panel, to various treatments indicated on the
		abscissa.  We can conclude, with 95\% confidence, that the classifier
		is performing better than chance when $\hat{\theta}_\text{NB}$ 
		exceeds 0.168, indicated by the dotted line.
	}}
}
\end{figure*}

In the language of computer science, $\mathcal{A}$ is a classifier performing
a binary classification.  The measure $\theta$ can range between 0 and 1, and 
indicates how much better the performance of the best possible classifier is 
compared to a random guess. We intentionally leave the details of 
$\mathcal{A}$ unrestricted because the theoretical value of $\theta$ should 
depend on the inherent differences between the populations, rather than on 
the performance of a particular classifier.

In practice, some particular classifier $\mathcal{C}$ is tested (using e.g. 
cross-validation) yielding a statistical estimate of its performance 
$\hat{\theta}_\mathcal{C}$. This
$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
theoretical value of $\theta$, because there might 
exist some other classifier $\mathcal{C}'$ with 
$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
For our experiment, we use a Naive Bayes classifier because it is easy to
implement and performs well across a broad range of classification tasks.

To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice 
$\mathcal{C}$ is to be made between two options on the basis of worker 
outputs (e.g. whether or not to flag an image as inappropriate). Any such 
binary choice has the formal structure of a distinguisher that only considers 
the last of its three inputs. Thus, we can directly compare $\mathcal{C}$ to 
the optimal distinguisher, $\mathcal{A}$.  If, prior to knowing the input to 
$\mathcal{C}$, either of its outcomes is equally likely, then the worst 
possible bias that priming can introduce is bounded above by $\theta$. 
This means that $\hat{\theta}_\mathcal{C}$ estimates a 
lower bound for the worst-case bias introduced in a binary 
decision that provides a full bit of information, made on the basis of worker 
outputs, when one failed to control for the corresponding priming treatments.
\subsection*{Experimental Setup}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

	\caption{ \footnotesize{ 
		Workers were uniformly randomly assigned to one of the 
		treatments listed above. 
		The full funder names used were 
		``The Global Foundation for Cultural Recognition'' and 
		``The National Foundation for Nutritional Awareness''.  
		The ambiguous, cultural, and ingredients initial image sets are shown 
		in \textbf{Figs. S2}, \textbf{S3}, and \textbf{S4}.
	}}
	\label{table:1}
\end{table}
We solicited 900 MTurk workers to perform an image-labeling task relating to
food and culture.  The workers were randomly assigned to one of seven 
treatments shown in \textbf{Table 1}.  Depending on their treatment, workers were then shown the 
name of a research funder, or this step was skipped.
Next, workers were shown ten images, one at a time and were required to provide
five labels for each.  For the purpose of analysis, we divide the images
into \textit{initial} and \textit{test} sets, comprising respectively the 
first five and last five images.  From the perspective of the worker, there 
was no distinction or interruption between the initial and test sets. 
Depending on the treatment, one of three initial image sets was chosen, but
the test set was always the same.

The test image set comprised images containing prepared meals and featured a 
prominent, identifiable culture (see \textbf{Fig. S1}).
To identify the initial image sets, we use the names ``ambiguous'', 
``cultural'', and ``ingredients''.  The ambiguous set was chosen to
be similar to the test set, in the sense that it consisted of
images of prepared meals (see \textbf{Fig. S2}),  but its cultural 
features were less prominent.  The cultural set featured 
iconic cultural scenes, but no food at all (see \textbf{Fig. S3}).  Images from 
the ingredients set depicted separated ingredients, but, 
like the ambiguous set, avoided prominent cultural features (see 
\textbf{Fig. S4}).
\subsection*{Results}
\paragraph{Inter-task priming was strong, while framing was weak.}
We tested for priming effects using our algorithmic definition, implemented 
with a Naive Bayes classifier.  The classifier's accuracy
in cross-validations involving each pair of treatments is shown in 
\textbf{Fig.1}.

With some exceptions, the classifier performed significantly better 
than chance when distinguishing treatments that had different initial tasks.  
This demonstrates that inter-task effects were strong. Of the sixteen 
treatment pairs having different initial tasks, the classifier was unable to
distinguish treatments significantly better than chance in three cases.
Each cases involved distinguishing treatments having the ambiguous and 
ingredients set.  Later we discuss the similarity between image sets, and 
we will argue that this is because the ambiguous and ingredients sets are 
similar.

\begin{figure*}
	\centering{
		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
	\caption{\footnotesize{
		\textbf{A}) Percent label composition (culture- vs food-oriented 
		labels) for 
		various images and treatments.  
		\textbf{B}) Relative specificities of treatments
		indicated along the abscissa compared to those indicated above the 
		plot.  The size of the bar indicates how much more specific
		the labels from one treatment are compared to the other, and points 
		toward in the direction of the more specific treatment.  Error bars
		indicate 95\% confidence intervals.
	}}
}
\end{figure*}
In contrast, the classifier never performed significantly better than chance
when distinguishing treatments that differed only in framing.  Thus, framing 
effects were rather weak.  In fact, framing effects were generally weak in
our results, so we omit treatments involving framing from the remainder of
our presentation to save space.  We encourage the interested reader to look
at the results for these treatments in the supplementary material.
\paragraph{Earlier tasks orient workers' focus during later tasks.} 
Since the initial images were chosen to emphasize either food (ingredients set)
or culture (cultural set), we looked for effects on the number of culture- and 
food-oriented labels that workers attributed to the test image set.

@@

\begin{figure}
	\centering{
	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
	\caption{\footnotesize{
		\textbf{A}) Difference in priming between \textsc{ambg} and 
		$\textsc{cult}_{img}$ measured based on the accuracy of a Naive Bayes 
		classifier during cross-validation, when trained on labels from the
		test images indicated along the abscissa.
		\textbf{B}) Excess cultural orientation of labels attributed to
		the test images indicated on the abscissa, by workers from
		$\textsc{cult}_{img}$ relative to those attributed by workers from
		\textsc{ambg}, calculated using \textbf{Eq. 3}.  Error bars indicate
		95\% confidence intervals.
	}}
}
\end{figure}
When we tallied labels attributed to the first image of the test set, 
we found that workers from $\textsc{cult}_{img}$ produced significantly 
more culture-oriented labels and less food-oriented ones than those from
\textsc{ambg}
(see \textbf{Fig. 2A}).  The inter-task effect was so strong that the 
proportion of food- and culture-oriented labels in $\textsc{cult}_{img}$ was
essentially the reverse of that in \textsc{ambg}.  However, the 
composition of labels attributed by $\textsc{ingr}_{img}$
was not significantly different from those attributed by \textsc{ambg}.  This 
shows that inter-task effects \textit{can} profoundly alter workers' focus. 
Again, we 
will argue later that the ambiguous and ingredients image sets are, in fact, 
quite similar.
\paragraph{Earlier tasks influenced workers' level of specificity.} 
Using the ontology described in the previous section, we can compare the 
specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more 
specific than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to 
$\ell_2$.  If there is no directed path between labels, we say they are  
\textit{non-comparable}.  For example, \texttt{tomato} was more specific than 
\texttt{food}, while \texttt{statue} and \texttt{food} were non-comparable.

@@

\begin{align}
	s_i(u,v) = \sum_{\ell \in u(i) } \;
	\sum_{m \in v(i)} 
	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
	\label{eq:worker-specificity}
\end{align}
where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
$m$, and 0 otherwise.
We then define the relative specificity of two treatments, $\mathcal{U}$ and 
$\mathcal{V}$, the $i$th image, denoted $S_i(\mathcal{U},\mathcal{V})$, to be 
the mean relative specificity of two uniformly drawn workers:  
\begin{align}
	\hat{S}_i(\mathcal{U},\mathcal{V}) = 
	\frac{1}{|\mathcal{U}| |\mathcal{V}|}
	\sum_{u \in \mathcal{U}} \;
	\sum_{v \in \mathcal{V}} \;
		s_i(u,v).
		\label{eq:specificity}
\end{align}

Looking at labels attributed to the first test image, we found that workers 
from \textsc{ambg} were more specific than workers from
either $\textsc{cult}_{img}$ or $\textsc{ingr}_{img}$.  When we compare 
$\textsc{cult}_{img}$ to $\textsc{ingr}_{img}$, we found that workers from
$\textsc{ingr}_{img}$ were more specific.  This shows that inter-task 
effects do substantially influence the specificity of labels that workers 
provide.  When we discuss image similarity, below, we will explore a possible
mechanism for this effect.
\paragraph{Inter-task effects ``wash out'' quickly.}  
It would stand to reason that, as workers proceed through the test images, 
priming from the initial images would be ``washed out'', diminishing the 
observed inter-task effects.
Looking at the classifier performance, $\hat{\theta}_\text{NB}$, with respect 
to the treatments \textsc{ambg} and $\textsc{cult}_{img}$, we find that 
performance does drop off dramatically after just the first image 
(see \textbf{Fig. 3A}).
This suggests that inter-task effects primarily arise between consecutive 
tasks, but that a residual effect can persist for at least five tasks (we 
note, however that although the classifier performance seemed better than 
chance for the fourth test image, this cannot be asserted with 95\% 
confidence).

Next we observed how inter-task effects on label composition (i.e. food- vs 
culture-oriented labels) evolve as workers proceed through test images.
We define the \textit{excess cultural orientation} as the number of 
culture-oriented labels minus the number of food oriented ones.  To 
meaningfully compare the excess cultural orientation between test images, we 
must, however, account for the fact that some images inherently carry more 
cultural content than others. In keeping with our notion of priming 
\textit{difference}, we calculate the excess cultural content for both 
$\textsc{cult}_{img}$ and \textsc{ambg}, and take their difference to be
the \textit{relative} excess cultural content, $\Delta_{cult}$.  Formally,
\begin{align}
	\begin{split}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right. \\
\left.	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
	\end{split}
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment.

We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
rapidly, remaining positive but not to a statistically significant extent
(see \textbf{Fig. 3B}).  
This is similar to the behavior of $\hat{\theta}_\text{NB}$, however, because
the statistical significance of $\Delta_{cult}$ dropped more quickly, 
$\hat{\theta}_\text{NB}$ appears to be a more sensitive measure of inter-task 
effects.
\paragraph{Inter-task similarity encourages more specific labels.}
To continue with the analysis, we seek a measure of image similarity.  The 
characterization of image content is a deeply complex issue that has been 
approached by many disciplines 
\cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}.
\textit{Perceptual similarity} is a particularly recalcitrant concept.

However, in the present study, we are more interested how similar two 
sets of images are, \textit{with respect to the labeling task}, which is much
simpler to operationalize than general perceptual similarity.  Here, we 
measure image similarity by looking at the fraction of labels that they share. 
Formally, to measure the similarity between two \textit{sets of images}, $X$ 
and $Y$, we compute the Jacquard index between the sets of labels attributed 
to them:
\begin{align}
	\text{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)},
\end{align}
\begin{table}
\centering
\begin{tabular}{ l  s s s s}

@@

\end{tabular}
\caption{\footnotesize{
Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
}}
\label{table:2}
\end{table}
where $L(X)$ denotes the set of labels attributed to $X$.

>>>>

%%%%%%%%%%
% Section Numbers
% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0} %%%%%%%%%%
\title{Inter-Task Effects Induce Bias in Crowdsourcing}
\author{Edward Newell\footnote{bla} \and Derek Ruths\\
School of Computer Science, McGill University, Montreal, Canada\\
$^*$\texttt{edward.newell@mail.mcgill.ca}\\
}
%%%%%%%%%%
% Body of Paper Begins
\begin{document}

\maketitle
\section*{Abstract}
Microtask platforms allow researchers to engage participants quickly and 
inexpensively.
Workers on such platforms probably perform many tasks in succession,
so we investigate interactions between earlier tasks and later ones, which we 
call \textit{inter-task} effects.  
Existing research investigates many task design factors, such as 
\textit{framing}, on the quality of responses, but to our knowledge, does not 
address inter-task effects.  
We used a canonical image-labeling task on Amazon Mechanical Turk 
to measure the impact of inter-task and framing effects on the focus and 
specificity of labels that workers provide.
We found that inter-task effects had a much stronger impact than framing, 
and that workers provided more specific labels when labeling 
a series of images that were similar to one another.

\paragraph{Keywords:} priming, framing, crowdsourcing.
\section*{Introduction}
Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis,Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a fast and cheap means to engage experimental 
participants in a research 
setting \cite{snow2008cheap}.

@@

Here, we highlight an important way in which HPUs differ from CPUs, with 
serious implications for the design of tasks.  It is well-known that people 
are subject to priming effects 
\cite{BJOP1796,No2007,beller1971priming} and, in particular, task-repetition effects
\cite{Gass1999549,sohn2001task}.  
We investigate the effect that previously completed tasks have on workers'
responses during subsequent ones. We call such effects 
\textit{inter-task effects}.  Inter-task effects would amount to a kind of
\textit{hysteresis}, meaning that HPU output is not only a function of the 
current input, but also of the history of inputs.

There has been considerable investigation into the factors that affect the 
quality and quantity of micro-task completion.  These include the level of 
pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, screening of 
workers \cite{paolacci2010running}, and user-interface design 
\cite{Finnerty2013}.  Researchers have also investigated \textit{framing}, 
by testing the effects of disclosing the workflow context 
\cite{Kinnaird2012281}, and the purpose of tasks 
\cite{chandler2013breaking}.  To our knowledge, no study has investigated 
inter-task effects.

We investigated inter-task effects on the MTurk platform, using image-labeling 
tasks, one of the most common kinds of tasks on MTurk
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  
Workers were required to label images featuring 
food and culture.  We regard these tasks as consisting of an 
\textit{initial} and a \textit{test set}, but, crucially, no
distinction was made between these sets from the view of the worker.
We varied the images in the initial tasks, while keeping those in the test set 
the same, to analyze the effects that the initial tasks had on the 
content and specificity of labels attributed in the test set.

As a point of comparison, we subjected some groups of workers to a kind of
\textit{framing}, by disclosing a fictitious, semantically-loaded name for 
the requester funding the tasks.
The names were chosen to suggest the requester's interest in a specific 
aspect of the image content.  We expected this would cause workers 
to provide more labels, and greater specificity, relating to this 
``preferred'' content.

Surprisingly, we found that inter-task effects were much stronger than
framing.  Our results show that initial tasks can significantly alter the 
focus of worker's labels.  Interestingly, we find that inter-task
effects can be used to induce greater specificity.  Our results suggest that
workers attribute more specific labels when labeling a series of images that
that are more similar to one another.  This suggests that careful 
consideration should be given to the bundling of tasks when designing a study 
using a microtask platform.

\subsection*{Experimental Setup}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Initial Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

	\caption{ \footnotesize{ 
		Workers were assigned uniformly at random to one of the 
		treatments listed above. 
		The full funder names used were 
		``The Global Foundation for Cultural Recognition'' and 
		``The National Foundation for Nutritional Awareness''.  
		The ambiguous, cultural, and ingredients initial image sets are shown 
		in \textbf{Figs. S2}, \textbf{S3}, and \textbf{S4}.
	}}
	\label{table:1}
\end{table}
We solicited 900 MTurk workers to perform image-labeling tasks relating to
food and culture.  The workers were randomly assigned to one of the treatments
shown in \textbf{Table 1}.  The treatments $\textsc{ingr}_{fund,img}$ and 
$\textsc{cult}_{fund,img}$ used (respectively) the image sets of 
$\textsc{ingr}_{img}$ and $\textsc{cult}_{img}$, but also 
incorporated framing.  The addition of framing did not have a substantial
impact on the results for these treatments, so we do not discuss 
$\textsc{ingr}_{fund,img}$ and $\textsc{cult}_{fund,img}$ further.

Workers from all treatments were shown brief instructions.  Depending on 
their treatment, workers were then 
shown the name of a research funder, or this step was skipped.
Next, workers were given a series of ten image-labeling tasks.  Each task 
required workers to privide five discriptive labels for an image.  For the 
purpose of analysis, we divided the tasks
into \textit{initial} and \textit{test} sets, comprising respectively the 
first five and last five tasks.  From the perspective of the worker, there 
was no distinction or interruption between the initial and test sets. 
Depending on the treatment, one of three sets of images was used for the
initial tasks, but the images in the test set were always the same.

The images from the test set contained prepared meals and featured a 
prominent, identifiable culture (see \textbf{Fig. S1}).
To identify the initial image sets, we use the names ``ambiguous'', 
``cultural'', and ``ingredients''.  The ambiguous set was chosen to
be similar to the test set, in the sense that it consisted of
images of prepared meals (see \textbf{Fig. S2}),  but its cultural 
features were less prominent.  The cultural set featured 
iconic cultural scenes, but no food at all (see \textbf{Fig. S3}).  Images from 
the ingredients set depicted separated ingredients, but, 
like the ambiguous set, avoided prominent cultural features (see 
\textbf{Fig. S4}).
\subsection*{Results}
\begin{figure*}
	\centering{
		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
	\caption{\footnotesize{
		\textbf{A}) Percent label composition (culture- vs food-oriented 
		labels) for 
		various treatments.  
		\textbf{B}) Relative specificities of treatments,
		indicated along the abscissa, compared to those indicated above the 
		plot, according to \textbf{Eq. 2}.  The size of the bar indicates how 
		much more specific
		the labels from one treatment are compared to the other, and points 
		toward the more specific treatment.  Error bars
		indicate 95\% confidence intervals.
	}}
}
\end{figure*}

\paragraph{Earlier tasks oriented workers' focus during later tasks.} 
Since the initial images were chosen to emphasize either food (ingredients set)
or culture (cultural set), we looked for effects on the number of culture- and 
food-oriented labels that workers attributed to the test image set.

@@

When we tallied labels attributed to the first image of the test set, 
we found that workers from $\textsc{cult}_{img}$ produced significantly 
more culture-oriented labels and less food-oriented ones than those from
\textsc{ambg} (see \textbf{Fig. 1A}).  The inter-task effects were so 
strong that the proportion of food- and culture-oriented labels in 
$\textsc{cult}_{img}$ was essentially the reverse of that in \textsc{ambg},  
showing that inter-task effects \textit{can} profoundly alter workers' focus.

\paragraph{Inter-task effects were stronger than framing effects.}
On the other hand, the labels attributed by 
$\textsc{ingr}_{fund}$ were not significantly different in composition from 
those attributed by $\textsc{cult}_{fund}$.  Workers from the
these treatments were told that the tasks were funded by, respectively, 
the ``Foundation for Nutritional Awareness'' and the ``Foundation for Cultural 
Recognition''.  We find it remarkable that inter-task effects were stronger
than those brought about by framing the tasks with reference to specific 
image content.

\paragraph{Earlier tasks influenced workers' level of specificity.} 
The ontology described in the previous section allows us to define the relative
specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more 
specific than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to 
$\ell_2$.  If there is no directed path between labels, we say they are  
\textit{non-comparable}.  For example, \texttt{tomato} was more specific than 
\texttt{food}, while \texttt{statue} and \texttt{food} were non-comparable.

@@

\begin{align}
	s_i(u,v) = \sum_{\ell \in u(i) } \;
	\sum_{m \in v(i)} 
	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
	\label{eq:worker-specificity}
\end{align}
where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
$m$, and 0 otherwise.
We can then define the relative specificity of two treatments, $\mathcal{U}$ 
and $\mathcal{V}$, with respect to the $i$th image, denoted $S_i(\mathcal{U},\mathcal{V})$, 
to be the mean relative specificity of two uniformly drawn workers:  
\begin{align}
	\hat{S}_i(\mathcal{U},\mathcal{V}) = 
	\frac{1}{|\mathcal{U}| |\mathcal{V}|}
	\sum_{u \in \mathcal{U}} \;
	\sum_{v \in \mathcal{V}} \;
		s_i(u,v).
		\label{eq:specificity}
\end{align}

The relative specificities of various treatments, based on \textbf{Eq. 2},
are shown in \textbf{Fig. 1B}.  We found that workers 
from \textsc{ambg} were more specific than workers from
either $\textsc{cult}_{img}$ or $\textsc{ingr}_{img}$.  Comparing
$\textsc{cult}_{img}$ to $\textsc{ingr}_{img}$, we found that workers from
$\textsc{ingr}_{img}$ were more specific.  This shows that inter-task 
effects do substantially influence the specificity of labels that workers 
provide.  We will return to this point below, where we propose a mechanism to 
explain these differences in specificity.

\paragraph{Inter-task effects ``washed out'' quickly.}  
It would stand to reason that, as workers proceed through the test images, 
priming from the initial images would be ``washed out'', diminishing the 
observed inter-task effects.

\begin{figure}
	\centering{
	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture_cut_for_hcomp.pdf}
	\caption{\footnotesize{
		Excess cultural orientation ($\Delta_\mathbf{cult}$) of labels 
		attributed by $\textsc{cult}_{img}$ relative to those attributed by 
		\textsc{ambg} 
		($\Delta_\mathbf{cult}$ is defined in \textbf{Eq. 3}).  Error bars 
		indicate 95\% confidence intervals.
	}}
}
\end{figure}
To investigate the evolution of inter-task effects, we define the 
\textit{excess cultural orientation} to be the number of 
culture-oriented labels minus the number of food oriented ones.  This measures
how culture-oriented a given image is.  Of course, we must account for the 
fact that some images inherently carry more 
cultural content than others. In keeping with our notion of priming 
\textit{difference}, we calculate the excess cultural content for 
both $\textsc{cult}_{img}$ and \textsc{ambg}, and take their difference to be
the \textit{relative} excess cultural content, $\Delta_{cult}$.  Formally,
\begin{align}
	\begin{split}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right. \\
\left.	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
	\end{split}
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment.

We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
rapidly, remaining positive but not to a statistically significant extent
(see \textbf{Fig. 2}).

\paragraph{Inter-task similarity encouraged more specific labels.}
To continue with the analysis, we sought a measure of image similarity.  The 
characterization of image content is a deeply complex issue that has been 
approached by many disciplines 
\cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}.
However, in the present study we are more interested how similar two 
sets of images are, \textit{with respect to the labeling task}, which is
simpler to operationalize than general perceptual similarity.  For this purpose
we measured the similarity between two sets of images by looking at the 
fraction of labels that they shared. 
Formally, to measure the similarity between two \textit{sets of images}, $X$ 
and $Y$, we computed the Jaccard index between the sets of labels attributed 
to them:
\begin{align}
	\text{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)},
\end{align}
where $L(X)$ denotes the set of labels attributed to $X$.

\begin{table}
\centering
\begin{tabular}{ l  s s s s}

@@

\end{tabular}
\caption{\footnotesize{
Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
}}
\label{table:2}
\end{table}

The pairwise similarities of the image sets are presented in \textbf{Table 2}. 
In particular, we draw the reader's attention to the similarity between the 
three initial sets and the test set.  The ambiguous set was the most similar 
to the test set, followed by the
ingredients set, while the cultural set was most different.
Note the correspondence between these degrees of similarity and the ensuing 
relative specificity of labels: the more similar the 
initial images were to those in the the test set, the more 
specific were the labels attributed to the test set  (c.f. \textbf{Fig. 1B}).
